Gozde and Liora's Replication Code

### 2015-05-13 response_to_reviewers.Rmd

Extension Edits:

1) We improved our logit link function in line with Matt's comment (line 93): we gave better names for arguments and outputs; we removed redundant code which created the link function for each model. 
2) Following Matt's suggestion (line 95), we graphed the range in predicted probabilities to better present the very little variation in predictions for all three models. The differences between the graphs for each model also made us realize the connection between plotted probabilities and the separation plots. 
3) Per Andres's comment (line 144) about the use of interactions in model 3, we added furher documentation. Here we decided to use interactions between contextual variables following the author's original model. 
4) Following Matt's question about the multi-level model, we added a note on this point. While we were interested in visualizing the predictive power of all three theories in our extension, we acknowledge that the original model's multi-level structure (individuals nested into election contexts in various countries) is a better way to analyze extreme-right vote intention for each individual.

5) In response to Matt's suggestion, we attempted (with varying levels of success) other diagnostics on our three models.  We created binned residuals plots and also attempted to compare predicted probabilities for extreme cases.

Attempting these edits has improved both our code and our thinking about the theoretical and empirical puzzles in this paper.  Again, many thanks to all the reviewers for their comments and suggestions.
